Practical Optional Types for Clojure

### 2015-02-21 intro.tex
add macro for core.typed

In the remainder of this paper, we describe Typed Clojure's central
innovations, including Java interoperability, multimethods, and
heterogenously-typed immutable maps, following an example-driven
presentation in Section~\ref{sec:overview}. We then incrementatlly
present a core calculus for Typed Clojure covering all of these
features together in Section~\ref{sec:formal} and prove type
soundness(section \ref{sec:sound}). We then discuss the full
implementation of Typed Clojure, dubbed \texttt{core.typed}, which
extends the formal model in many ways, and the experience gained from
its use in Section~\ref{sec:exp}. Finally, we discuss related work and
conclude.

>>>>

In the remainder of this paper, we describe Typed Clojure's central
innovations, including Java interoperability, multimethods, and
heterogenously-typed immutable maps, following an example-driven
presentation in Section~\ref{sec:overview}. We then incrementatlly
present a core calculus for Typed Clojure covering all of these
features together in Section~\ref{sec:formal} and prove type
soundness(section \ref{sec:sound}). We then discuss the full
implementation of Typed Clojure, dubbed \coretyped{}, which
extends the formal model in many ways, and the experience gained from
its use in Section~\ref{sec:exp}. Finally, we discuss related work and
conclude.
